
\scriptsize 
\begin{spacing}{1}
\begin{longtable}{m{30mm}|m{90mm}|c @{\hskip 1mm} c}
\hline
Title & Description & Proposal & Result\\
\hline
\hline
\endhead
 Actions on cooperation. & Promote shared projects with other reference cities to: share experience, visibilize the world that it is possible to do it in a different way with example around the world. & 2376 & 5055, 5927 \\ \hline
 Start the "Refuge" plan & The District of the Eixample undertakes to develop the "Refuge" plan and to promote the involvement of entities and groups in the different neighborhoods in this plan. & 274 & 5055  \\ \hline
 Initiatives with refugees. & creation of shelters, reception. & 2293 & 5055, 5932  \\ \hline
 Attention to refugees. & Barcelona City Refuge, neighborhood committed to the refugees, platform creation or support group & 2358 & 5055, 5932  \\ \hline
 Participate in international networks to support the rights of migrants & It strives to coordinate and to be part of the international initiatives in defense of the rights of the migrants, as much at institutional level as citizen. & 8505 & 5723  \\ \hline
 Commit Barcelona to the global fight for human rights & Increase efforts to make public debate, support organizations that work for regional justice and initiate processes of international impact to contribute to the achievement of a system of global governance that protects the human rights of people and peoples in the Euro-Mediterranean region. & 1023 & 5723  \\ \hline
 Educate for global justice & Progressively increase the weight of education for global justice.We must move towards an identified citizenry with a solidarity Barcelona and committed to global justice, and involved in the different transnational networks that work in this regard from civil society. & 1025 & 5725  \\ \hline
 Report international cooperation projects & disseminate good practices, horizontally and vertically, to share and improve the actions that are carried out & 1838 & 5725  \\ \hline
 Insubmission to TTP, TTIP and TISA. & Declare Barcelona as a city insubmised in the treaties of the TTP, TTIP and TISA, to make a campaign for information and dissemination for the commerce of the proximity of this treaty and its involvement in trade. & 10327 & 5927 \\ \hline
 Renew the spaces and processes of participation and sensitization of the city's agents in matters of global justice & Taking into account the changes suffered during the last years in the set of actors related to global justice, it is advisable to review and search the most effective ways of co-participation between citizens, the sector, public institutions and the City Council. & 2961 & 5927 \\ \hline
 Exchange of good practices between European cities & Export and import activities and good practices that are working & 7536 & 5927 \\ \hline
 Develop a global action plan and justice 2016-2020 & The outer action plan will outline the guidelines of the city's foreign policy in all its dimensions (governance, relations with other international cities, international networks, economic relations, culture, cooperation, etc.).It is an instrument of definition and planning of the public policy of global justice, which is especially vigilant for the coherence of the external action of the municipal Government. & 2957 & 5927 \\ \hline
 Reinforce the policies of relations and international cooperation of the city council & Strengthen the relationship and cooperation of the city council with other cities around the world and its external projection in order to learn from the best practices and promote the development and inclusion experiences driven locally.Work in horizontal networks of cities and deepen development cooperation projects. & 1232 & 5927 \\ \hline
 Transition towards a model of cooperation aimed at global justice & Work on sensitization and solidarity actions. & 2112 & 5927 \\ \hline
 Measures on cooperation. & Promote a municipal cooperation network to act and move forward with the major issues that concern the State and Europe: the economic model, distribution of wealth, consumer culture, ecology, etc. & 2292 & 5929 \\ \hline
 Coordinate and strengthen the international networks present in the city & Develop a work strategy that strengthens the principles and values ​​that define the municipal cooperation, based on the fact that in Barcelona there are headquarters and general secretariats of the main international municipal networks, and it is the city that participates in a greater number of international networks, both generalist and thematic (in key areas such as the environment, the fight against climate change, local governance, education, etc.).Guarantee also that this know how to make use of the economic fabric of the city. & 2959 & 5929 \\ \hline
 Increase support for all refugees & Mitjans school plan, family plan ... & 6142 & 5932 \\ \hline
 Incorporate LGBT perspective in the refugee support plan & Incorporate the LGTBI perspective in the refugee support plan and take into account its rights as LGBT people. & 10235 & 5932 \\ \hline
 Motion for refugee reception & Join the motion approved by the District Council of the District of Sants-Montjuic by the Senate Sectoral Council. & 5113 & 5932  \\ \hline
 Create reception spaces for immigrant and refugee population & Often the population that arrives in Barcelona fleeing poverty or conflicts in their countries is relocated.You need to create reception and education spaces where you can meet your first needs. & 6744 & 5932 \\ \hline
 Help Syrian people & Barcelona should give an example and collaborate with economic funds with pro-active open arms every day where its volunteers play their lives saving people who flee from the war in Syria.It is unfortunate as a cosmopolitan and open city Enacara has not acted in this great humanitarian crisis with concrete facts and easy to carry out & 3193 & 5932\\ \hline
 Barcelona city refuge in Sarrià - Sant Gervasi & Support the proposal "start the Barcelona city refugee plan" and let it be set up in this district. & 6255 & 5932 \\ \hline
 Start the plan "Barcelona, ​​a city refuge" & Start up an operational and strategic plan for the reception of the city.To create a stable and permanent support structure for refugees and asylums that is complementary to state programs, with their own criteria and in collaboration with entities that work on the subject.Pay special attention to asylum seekers who are left out of the state social support program.Create a city-to-city cooperation plan for the high-density municipalities receiving refugees and migrants. & 2962 & 5932 \\ \hline
 Withdrawal of the EU flag to any official entity in Barcelona & Withdrawal of the EU flag to any official entity of Barcelona as a sign of rejection for the lamentable action that is being carried out with the refugees & 6214 & 5932 \\ \hline
 Leadership of Barcelona host city. & The city of Barcelona, ​​with the city council at the head, leads the reception of refugees. & 8678 & 5932 \\ \hline
 Create a bank of resources for refugees at the level of the District connected to the Generalitat in two levels (reception and awareness) & The reception of refugees in the city must be planned, work in conjunction with the Generalitat and establish measures to: - The reception (accommodation, support, language, etc.) - Awareness (educational centers and citizenship in general) & 6050 & 5932 \\ \hline
 Participation in the Social Area Barcelona City Refuge & Participation in the Social Area Barcelona City Refuge & 1824 & 5932 \\ \hline
 Engage in the reconstruction of the city of Kobane, in the Kurdish region of Syria. & The city of Kobane was a battle scene of the Kurdish militia against Daesh (Islamic state).The battle was won but the city was destroyed by 70\%.Now you have to rebuild it.Thus emancipating policies in the Middle East are supported and conditions are created so that the population can return instead of fleeing to Europe. & 7287 & 5933 \\ \hline
 Boost Barcelona as the capital for peace in the Mediterranean & Promote cooperation agreements and transnational twinning with cities considered as the arrival points of refugees and migrants from the Mediterranean in coordination with existing networks and the Refugee Cities Network.Increase the efforts to make a public debate, support organizations that work for regional justice and initiate processes of international impact to contribute to the achievement of a global governance system that protects the human rights of people and the towns in the region. & 2963 & 5933 \\ \hline
\caption{Global Justice proposals.}
\label{tab:negatives} \\
\end{longtable}
\end{spacing}
\normalsize