\scriptsize %%%%%%%%%%%  smaller font size %%%%%%%%
\begin{spacing}{1}
\begin{longtable}{m{30mm}|m{85mm}|c|m{15mm}}
\hline
Title & Description & Proposal & Category  \\
\hline
\hline
\endhead
 Visibilize the cultural activities of the district in the city circuit & Promote proposals and cultural productions that take place in Nou Barris and propose one of these projects in the city to enter the cultural map of Barcelona. & 1052 & Culture  \\ \hline
 Open the exhibition spaces of the district to the entities and the neighborhood of the territory & Generate competition bases to open the four exhibition halls of the city to all kinds of proposals, to turn them into spaces to promote popular and cultural exhibits, as well as personal artistic proposals. & 3053 & Culture  \\ \hline
 Promote the participation of the families of students in cultural activities & Promote the participation of the families of students in cultural activities. & 9052 & Culture  \\ \hline
 Commercial axis as a vehicle for cultural dissemination & Commercial axis: entities and stores as vehicles of cultural dissemination The dissemination can be done through the shops & 4348 & Culture \\ \hline
 Coordination of the networking of large cultural facilities and those with entities, communities and collectives, both in the cultural and academic worlds & Encourage networking and new collaborative projects between libraries, civic centers, cultural entities, large museums or research and creation spaces to ensure the maximum circulation of contents and artistic practices. & 2891 & Culture \\ \hline
 Coordination of the city's culture & Create a brand that coordinates the entire cultural offer in Barcelona, ​​both from public and private entities. & 3372 & Culture \\ \hline
 The libraries of the District as cultural agents of knowledge of the territory. & Activities organized by the libraries and other entities to make known the Heritage and the History of the District to the users. & 5810 & Culture \\ \hline
 Day We create health to reduce inequalities: Go to the causes of causes. & To give importance to the diagnoses to go to the causes of the causes. & 10897 & Health \\ \hline
 Mental health improvement projects & Encourage projects of entities in the sector to improve the mental health of the population. & 538 & Health \\ \hline
 Strengthen the network of Mental Health for children and adolescents & Strengthen the network of Mental Health for children and adolescents to support situations of crisis and consultation in schools and caregivers.To attend more quickly and to prioritize infant at high risk. & 6484 & Health \\ \hline
 Mental Health Plan: Support programs for professionals. & Training and specific resources for professionals in childhood and adolescence.Areas of coordination and work with young and homeless spaces. & 10828 & Health \\ \hline
 Speeches of talks by neighborhoods of health professionals & Make a talk series of health professionals with entities, Neighborhood Associations etc.To improve the information. & 8133 & Health \\ \hline
 Day We create health to reduce inequalities: symbiotic interventions. & Symbiotic interventions where different populations and needs benefit mutually from their strengths, being voluntary or new sources of employment. & 10915 & Health \\ \hline
 Health in Barcelona: Review the patient care model. & To train professionals from the empowerment model.Go from the assistance model to an empowering model.Do not generate employee dependence. & 10868 & Health \\ \hline
 Day We create health to reduce inequalities: More resources are needed so that professionals can do more work and community actions. & For example, more home care, street work, community mediation, etc ...). & 10895 & Health \\ \hline
 Increase medical assistance - Horta Guinardó. & It is proposed to increase the number of doctors to offer a better medical assistance service, especially in general medicine. & 8681 & Health \\ \hline
 Reopen / create the services previously referred to as 'family planning' & The life cycle of women has sexual characteristics specific to the potential and / or reproductive activity: menstruation, pregnancy, menopause are phases, not diseases, which should be able to monitor proximity to all neighborhoods.Women's sexual health centers would be very useful. & 1684 & Health \\ \hline
 Training in health workers in functional diversity & Training health workers as gynecologists in functional diversity so that they can break a little with the taboos of this group and be able to accompany them in a more integral way & 5050 & Health \\ \hline
 Ensure the existence of quality public services and specific services for young people, incorporating a gender perspective and respect for affectivosexual diversity, both in primary care centers and in educational centers & Promotion of training from the ASPB to professionals in the field of medicine, especially those that work around the ASSiR in LGBTI issues, gender perspective, sexual diversity Maintain and expand the specialized care services of the young people taking into account gender perspective, gender and sexual diversity within the CAPs. & 8435 & Health \\ \hline
 Training in interculturality for health professionals. & Training in interculturality for health professionals. & 10920 & Health \\ \hline
 Comprehensive community health plan, women, the elderly and the immigrant population & Create a Health Table equipped with your own resources & 537 & Health \\ \hline
 Guarantee the stability of budgets and recovery of health services and outsourced services: & Recover all those sanitary services that have been eliminated due to the cuts and all the services that have been derived to private entities.https://decidim.barcelona/proposals/reduccio-de-les-externalizaciones-i-les-privatizaciones-de-serveis-sanitaris & 8136 & Health \\ \hline
 Incorporate LGBT perspective in the refugee support plan & Incorporate the LGTBI perspective in the refugee support plan and take into account its rights as LGBT people. & 10235 & Host city \\ \hline
 Initiatives with refugees. & creation of shelters, reception. & 2293 & Host city \\ \hline
 Attention to refugees. & Barcelona City Refuge, neighborhood committed to the refugees, platform creation or support group & 2358 & Host city \\ \hline
 Start the "Refuge" plan & The District of the Eixample undertakes to develop the "Refuge" plan and to promote the involvement of entities and groups in the different neighborhoods in this plan. & 274 & Host city \\ \hline
 Start the plan "Barcelona, ​​a city refuge" & Start up an operational and strategic plan for the reception of the city.To create a stable and permanent support structure for refugees and asylums that is complementary to state programs, with their own criteria and in collaboration with entities that work on the subject.Pay special attention to asylum seekers who are left out of the state social support program.Create a city-to-city cooperation plan for the high-density municipalities receiving refugees and migrants. & 2962 & Host city \\ \hline
 Participation in the Social Area Barcelona City Refuge & Participation in the Social Area Barcelona City Refuge & 1824 & Host city \\ \hline
 Create a bank of resources for refugees at the level of the District connected to the Generalitat in two levels (reception and awareness) & The reception of refugees in the city must be planned, work in conjunction with the Generalitat and establish measures to: - The reception (accommodation, support, language, etc.) - Awareness (educational centers and citizenship in general) & 6050 & Host city \\ \hline
 Installation of gymnastics devices in the public parks of La Marina - Zona Franca. & Promote young people's sports practice. & 4318 & Sports \\ \hline
 Comprehensive reform of the Municipal Narcís Hall Camp & Continue with the process of integral reform of the Narcí Sala Municipal Camp and execute phases 2, 3 and 4 during the years 2016, 2017 and 2018 respectively.This process will always count with the participation and supervision of the managing entity, which will also be revamped with provisional facilities while the works affect parts of the stadium. & 1918 & Sports \\ \hline
 Take advantage of the dimensions of the old soccer field in Santander street for sports that require large sizes & and avoid dividing it into small clues, since the opportunity that this great space is giving away is wasted & 5099 & Sports \\ \hline
 Coherence in municipal sports facilities with the environmental policies promoted by the City Council. & Be consistent in sports facilities with the policies promoted by the City Council, especially with the selective collection of waste. & 7991 & Sports \\ \hline
 Encourage sports programs for children and young people during the holiday season & Promote sports practice during holiday periods, in order to guarantee the rights to the access and the sporting practice of young people and children, regardless of their conditions and the territory in which they live, and to promote the reconciliation of family life. & 792 & Sports \\ \hline
 Creation of sports and play areas in the public space & Generate new areas of sports and play areas in the public space in order to promote a healthy, active and community life. & 708 & Sports \\ \hline
 Create a sports area for young people in the Free Trade Zone & In the face-to-face event that took place at the IES Montjuïc, the 4th ESO students proposed the creation of a sports area for young people in the Free Trade Zone & 7934 & Sports \\ \hline
 Adapt the maintenance of sports spaces to the volume of users. & In order to guarantee the proper maintenance of the equipment, adapt it to the volume of use of the equipment.Track in a specific and adapted way to each facility.Especially in the summer season. & 7996 & Sports \\ \hline
 Improve and transfer sports spaces & It is valued to promote health from these entities through the availability of these spaces.They put the example of the chromium of the youth house of the courts, which should be improved and give way to the football field & 6697 & Sports \\ \hline
 Children's Sports Festival & Promote the Children's Sports Festival as a showcase for sports activities and the different sports groups of Gràcia.Promote the participation of schools and school sports. & 40 & Sports \\ \hline
 Open more municipal sports facilities. & Open more municipal sports facilities.In the case of Poble Nou, they can only access Can Felipa, who perceive that it is saturated and has limited and inadequate facilities. & 4137 & Sports \\ \hline
 Reduction and adaptation of the quotas for municipal sports facilities. & Reduce access prices to municipal sports facilities.Adapt the quotas to the different groups, make specific quotas for families, large families, retirees, and other groups.Set the hour division into two strips.Universalise the price of the equipment.Flexible quotas to include a minimum service of activities. & 7999 & Sports \\ \hline
 Encourage and increase municipal information & Support the radio of Sants.To make campaigns for the dissemination and awareness of participation.Increase political transparency.More understandable information for citizens, nearby. & 5383 & Transparent government \\ \hline
 To achieve the full transparency and retention of accounts of public management & Recognize and facilitate the work of popular control initiatives, such as citizen observatories against corruption, transparency and good governance and promote a citizen advice that audits the proceedings of the district. & 6021 & Transparent government \\ \hline
 Prepare the District Transparency Plan & Design and launch a plan with information that is neat and easy to consult through the Internet, which allows you to know in detail the budgets, the use made of the public resources and the actions carried out by the Administration and its institutional representatives. & 1089 & Transparent government \\ \hline
 To achieve the full transparency and retention of accounts of public management & Recognize and facilitate the work of popular control initiatives, such as citizen observatories against corruption, transparency and good governance and promote a citizen advice that audits the proceedings of the district. & 6022 & Transparent government \\ \hline
 Change how the City Council operates internally on some fronts linked to the common good: strengthen the existing procommun communities, respecting their autonomy & As a general principle, support communities of the existing procommunication and / or technologies, instead of replacing them with the administration, promoting the consolidation or creation of communities that can be self-managed and allow them to be autonomous, They respect ethical questions and work for the common good. & 7423 & Transparent government \\ \hline
 Improvement in communication channels with the City Council. & Parity work sessions, e-Government, Open Data, Technology and politics, e-voting, information on right access to information, web where citizens can propose projects. & 2357 & Transparent government \\ \hline
 Develop an ethical code for elected officials and management personnel & Develop the code that aims to establish the principles and ethical values ​​and the rules of conduct that must be respected by the elected officials and municipal management personnel in the exercise of their functions, with the main purpose of guaranteeing efficient, complete management and transparent from the municipal administration. & 999 & Transparent government \\ \hline
 Enable an ethical mailbox & Enabling an ethical mailbox conceived as a tool for participation so that citizens can safely communicate to the City Council facts and behaviors that are contrary to an ethical management of the Administration. & 998 & Transparent government \\ \hline
 Portal of transparency & Publish the councilor's agenda, as well as its declaration of assets and interests;The declarations of goods and interests of District Counselors will also be published, and the District's estimates and investments will be made public. & 837 & Transparent government \\ \hline
 District communication plan & Write and execute the Communications Plan of the District of the Cortes in order to improve the tools that give logic, coherence, purpose and effectiveness to internal and external communication. & 502 & Transparent government \\ \hline
 Improve the information and accessibility of the websites of the City Council & Facilitate the knowledge of the activities, actions of the city council.Improve transparency. & 6140 & Transparent government \\ \hline
 Improve general communication and transparency on ongoing works and on the street & I still see works every day without knowing what they are doing (eg, a type of orchard street Mare de Deus de las Neus, we have a look at it from home, we do not know after 2 years that it is neither for whom). They still continue to do the works clear poster that announces that something will be done soon, for whom, the final result, the financing. & 8583 & Transparent government \\ \hline
 waiting room for saints & The Citizen Attention Office dl district of Sants has a ludic waiting room for the large number of citizens who are going to take steps.There is no maximum capacity or limit.There are also windows and therefore not natural light.There is air conditioning but when there are so many people in the summer it is not noticeable.It's small and claustrophobic.You need a larger room & 1298 & Transparent government \\ \hline

\caption{Set of correctly clustered proposals.}
\label{tab:positives} \\
\end{longtable}
\end{spacing}
\normalsize